Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2014-01-28 paper/paper.tex
Reword experiments section

\section{Experimental Results}
\label{sec:experiments}
We implemented our fully automatic synthesis procedure as the {\sc kalashnikov} tool.  The implementation consists
of around 600 lines of \newC and 600 lines of Python.  To evaluate the tool we used the 25 bitvector
programs from~\cite{brahma} and~\cite{brahma-icse}.  The majority of these are ``bit twiddling hacks'' taken from
Hacker's Delight~\cite{hackers-delight}.  The code we used to perform the experiments, along with the
benchmarks, is available at \texttt{http://www.cprover.org/kalashnikov}.  As a backend solver, we used
{\sc CBMC}~\cite{cbmc-website} at SVN revision r3545, with Glucose 3.0~\cite{glucose-paper} as the SAT solver.
We performed our experiments on a 4-core, 2.40\,GHz Xeon E5-2665 with 32\,GB of RAM.

@@

The results of our experiments are shown in Fig.~\ref{fig:results-table} and Fig.~\ref{fig:icse-results-table}.
The tables include the runtime for each tool, the number of lines in the synthesised program and whether
{\sc Brahma} was able to complete the synthesis completely automatically (the ``Aut.''~column).  A blank
in the ``Aut.''~column means that {\sc Brahma} was able to synthesise the program automatically, and a \xmark
\,means that user assistance was required.
On both sets of benchmarks, the results can be broadly divided into three categories:

\paragraph{\bf {\sc Kalashnikov} synthesises a shorter program than {\sc Brahma}:}
This happens in 4 of the 29 cases.  This case is illustrated by benchmark p29, shown in Fig.~\ref{fig:obfuscated}.
The specification here is a piece of obfuscated code taken from the Conficker worm~\cite{conficker}, and
our goal is to synthesise an equivalent program which is easier to understand.  The obfuscated code
uses several tricks, including an apparently unbounded loop.  {\sc Brahma} is able to
produce an equivalent program consisting of four instructions using shifts and addition, whereas {\sc kalashnikov}
is able to produce the minimal program \verb|y * 45|.  It is also worth noting that the specification
fed to {\sc kalashnikov} was just the obfuscated code, with no further preprocessing needed.
\paragraph{\bf {\sc Kalashnikov} is unable to synthesise a program:}
This happens in 8 of the 29 cases.  In each case, {\sc Brahma} needs user guidance to synthesise the program.
The existence of instances that are beyond the reach of current automatic
methods, and thus require manual intervention, is to be expected.
% A total of 8 tests fall into this category.
\paragraph{\bf {\sc Brahma} and {\sc Kalashnikov} both synthesise minimal programs:}
In the remaining cases, both {\sc brahma} and {\sc kalashnikov} are able to produce
minimal programs.  We performed a Mann-Whitney U-test (see Fig.~\ref{fig:stats-table})
to determine whether there was a significant difference
in the speed of the two tools.  The test was unable to reject the null hypothesis
(that the tools are equally fast) at the p=0.05
level, i.e. there is no statistically significant difference in the speed of
the two tools on this set of benchmarks.

>>>>

\section{Experiments}
\label{sec:experiments}
\subsection{Experimental Setup}
We implemented our fully automatic synthesis procedure as the {\sc kalashnikov} tool.  The implementation consists
of around 600 lines of \newC and 600 lines of Python.  To evaluate the tool we used the 25 bitvector
programs from~\cite{brahma} and~\cite{brahma-icse}.  The majority of these are ``bit twiddling hacks'' taken from
Hacker's Delight~\cite{hackers-delight}.  The code we used to perform the experiments, along with the
benchmarks, is available at \texttt{http://www.cprover.org/kalashnikov}.  As a backend solver, we used
{\sc CBMC}~\cite{cbmc-website} at SVN revision r3545, with Glucose 3.0~\cite{glucose-paper} as the SAT solver.
We performed our experiments on a 4-core, 2.40\,GHz Xeon E5-2665 with 32\,GB of RAM.

@@

\subsection{Experimental Results and Analysis}
The results of our experiments are shown in Fig.~\ref{fig:results-table}.
Column 1 shows the runtime reported for each benchmark in \cite{brahma}, column 2
shows the number of instructions in the synthesised program, and column 3 contains a \xmark when
{\sc Brahma} needed user assistance to solve a benchmark.
Columns 4 through 7 show the same information, but with the data taken from~\cite{brahma-icse}.
Column 5 shows the runtimes for the version of {\sc Brahma} from~\cite{brahma-icse} which
implemented the semibiased optimisation.
Finally, column 8 shows the runtime for {\sc Kalashnikov} and column 9 the number of instructions
in the program synthesised by {\sc Kalashnikov}.  The results can be broadly divided into
three categories, as follows:

\paragraph{\bf {\sc Kalashnikov} synthesises a shorter program than {\sc Brahma}:}
This happens in 4 of the 29 cases.  This case is illustrated by benchmark p29, shown in Fig.~\ref{fig:obfuscated}.
The specification here is a piece of obfuscated code taken from the Conficker worm~\cite{conficker}, and
our goal is to synthesise an equivalent program which is easier to understand.  The obfuscated code
uses several tricks, including an apparently unbounded loop.  {\sc Brahma} is able to
produce an equivalent program consisting of four instructions using shifts and addition, whereas {\sc kalashnikov}
is able to produce the minimal program \verb|y * 45|.  It is also worth noting that the specification
fed to {\sc kalashnikov} was just the obfuscated code, with no further preprocessing needed.
\paragraph{\bf {\sc Kalashnikov} is unable to synthesise a program:}
This happens in 8 of the 29 cases.  In each case, {\sc Brahma} needs user guidance to synthesise the program.
The existence of instances that are beyond the reach of current automatic
methods, and thus require manual intervention, is to be expected.
% A total of 8 tests fall into this category.
\paragraph{\bf {\sc Brahma} and {\sc Kalashnikov} both synthesise minimal programs:}
In the remaining cases, both {\sc brahma} and {\sc kalashnikov} are able to produce
minimal programs.  We performed a Mann-Whitney U test (see Fig.~\ref{fig:stats-table})
to determine whether there was a significant difference
in the speed of the two tools.  The test was unable to reject the null hypothesis
(that the tools are equally fast) at the p=0.05
level, i.e. there is no statistically significant difference in the speed of
the two tools on this set of benchmarks.
